The Title Goes Here with Each Initial Letter Capitalized

### 2018-04-16 2018/LeGo/LeGo.tex
Paper from LION

\begin{abstract}
In the present paper, a novel approach to the constructing of the test global optimization problems with non-convex constraints is considered. The proposed approach is featured by a capability to construct the sets of such problems for carrying out multiple computational experiments in order to obtain a reliable evaluation of the efficiency of the optimization algorithms. When generating the test problems, the necessary number of constraints and desired fraction of the feasible domain relative to the whole global search domain can be specified. The locations of the global minimizers in the generated problems are known a priori that simplifies the evaluation of the results of the computational experiments essentially. A demonstration of the developed approach in the application to well-known index method for solving complex multiextremal optimization problems with non-convex constraints is presented.

\keywords global optimization, multiextremal functions, non-convex constraints, test optimization problems, numerical experiments

\end{abstract}

\section{Introduction}

In the present paper, the methods for generating the global optimization test problems with non-convex constraints
\begin{eqnarray}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}}, \label{i_problem} \\
&D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\} \label{D}
\end{eqnarray}
are considered. The objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and the left-hand sides $g_i(y), \; 1\leq i \leq m,$ of the constraints are supposed to satisfy the Lipschitz condition
\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1. \]
with the Lipschitz constants unknown a priori. The analytical formulae of the problem functions may be unknown, i.e. these ones may be defined by an algorithm for computing the function values in the search domain (so called ''black-box''-functions). It is supposed that even a single computing of a problem function value may be a time-consuming operation since it is related to the necessity of numerical modeling in the applied problems (see, for example, \cite{Famularo}--\cite{Modorskii}).

The evaluation of efficiency of the developed methods is one of the key problems in the optimization theory and applications. Unfortunately, it is difficult to obtain any theoretical estimates in many cases. As a result, the comparison of the methods is performed by carrying out the computational experiments on solving some test optimization problems in most cases. In order to obtain a reliable evaluation of the efficiency of the methods, the sets of test problems should be diverse and representative enough. The problem of choice of the test problems has been considered in a lot of works (see, for example, \cite{Floudas}--\cite{Addis}). Unfortunately, in many cases, the proposed sets contain a small number of test problems, and it is difficult to obtain the problems with desired properties. And, the most important, the constraints are absent in the proposed test problems as a rule (or the constraints are relatively simple: linear, convex, etc.).

A novel approach to the generation of any amount of the global optimization problems with non-convex constraints for performing multiple computational experiments in order to obtain a reliable evaluation of the efficiency of the developed optimization algorithms has been proposed. When generating the test problems, the necessary number of constraints and desired fraction of the feasible domain relative to the whole search domain can be specified. In addition, the locations of the global minimizers in the generated problems are known a priori that simplifies the evaluation of the results of the computational experiments essentially.

@@

One generator for random samples of two-dimensional test functions has been described in \cite{Grishagin1978,Grishagin2016}. This generator produces two-dimensional functions according to the formula
\begin{eqnarray} \nonumber \label{VAG}
\varphi(y)= -&\left\{\left(\sum^{7}_{i=1}\sum^{7}_{j=1}A_{ij}g_{ij}(y)+B_{ij}h_{ij}(y)\right)^2+\right. \\
&\left.\left(\sum^{7}_{i=1}\sum^{7}_{j=1}C_{ij}g_{ij}(y)+D_{ij}h_{ij}(y)\right)^2\right\}^{1/2},\\ \nonumber
\end{eqnarray}
where $g_{ij}(y)=\sin(i\pi y_1)\sin(j\pi y_2)$, $h_{ij}(y)=\cos(i\pi y_1)\cos(j\pi y_2)$, $y=(y_1,y_2)\in R^2, \; 0 \leq y_1,y_2 \leq 1$, and coefficients $A_{ij}, B_{ij}, C_{ij}, D_{ij}$  are taken uniformly in the interval $[-1,1]$.

@@

\section{Some numerical results}

@@

The index method has been proposed and developed in \cite{Strongin2000,Barkalov2002}. The approach is based on a separate accounting for each constraint of the problem and is not related to the use of the penalty functions. According to the rules of index method, every iteration includes a sequential checking of fulfillment of the problem constraints at this point. The first occurrence of violation of any constraint terminates the trial and initiates the transition to the next iteration. This allows: (i) accounting for the information on each constraint separately and (ii) solving the problems, in which the function values may be undefined out of the feasible domain.  It should be noted, that the index method can be efficiently parallelized for accelerators \cite{Barkalov2015,Barkalov2016}.

@@

The developed approach allows generating any number of test global optimization problems with non-convex constraints for performing multiple computational experiments in order to obtain a reliable evaluation of the efficiency of the developed optimization algorithms. To develop the proposed approach further, the development of new test classes for the optimization problems of various dimensionalities is planned.

\bigskip

\textbf{Acknowledgments.} This study was supported by the Russian Science Foundation, project No 16-11-10150.

\begin{thebibliography}{99}

\bibitem{Famularo}
Famularo, D., Pugliese, P., Sergeyev, Ya.D.:A global optimization technique for checking parametric robustness. Automatica. 35, 1605--1611 (1999)

\bibitem{Menniti}
Kvasov, D.E., Menniti, D., Pinnarelli, A., Sergeyev, Ya.D., Sorrentino, N.: Tuning fuzzy power-system stabilizers in multi-machine systems by global optimization algorithms based on efficient domain partitions. Electric Power Systems Research. 78(7), 1217--1229 (2008)

\bibitem{Kvasov2015}
Kvasov, D.E., Sergeyev, Y.D.: Deterministic approaches for solving practical black-box global optimization problems. Advances in Engineering Software. 80, 58--66 (2015)

\bibitem{Modorskii}
Modorskii, V.Y., Gaynutdinova, D.F., Gergel, V.P., Barkalov, K.A.: Optimization in design of scientific products for purposes of cavitation problems.Solving Global Optimization Problems on GPU Cluster. In: Simos T.E. (Ed.) ICNAAM 2015, AIP Conference Proceedings. 1738, art. no. 400013 (2016)

\bibitem{Floudas} 
Floudas, C.A., et al.: Handbook of test problems in local and global optimization. Kluwer Academic Publishers, Dordrecht (1999)

\bibitem{Gaviano}
Gaviano, M., Kvasov, D.E., Lera, D., Sergeyev, Ya.D.: Software for generation of classes of test functions with known local and global minima for global optimization. ACM TOMS 29(4), 469--480 (2003)

\bibitem{Ali} Ali, M.M., Khompatraporn, C., Zabinsky Z.B.: A numerical evaluation of several stochastic algorithms on selected continuous global optimization test problems. J. Glob. Optim. 31(4), 635--672 (2005)

\bibitem{Addis} Addis, B., Locatelli, M.: A new class of test functions for global optimization. J. Glob. Optim. 38(3), 479--501 (2007)

\bibitem{Grishagin1978}
Grishagin, V.A.: Operating Characteristics of Some Global Search Algorithms. Problems of Statistical Optimization. 7, 198--206 (1978) [in Russian]

\bibitem{Grishagin2016} 
Gergel, V., Grishagin, V., Gergel, A.: Adaptive nested optimization scheme for multidimensional global search. J. Glob. Optim. 66 (1), 35--51 (2016)

\bibitem{Strongin2000}
Strongin, R.G., Sergeyev, Ya.D.: Global optimization with non-convex constraints. Sequential and parallel algorithms. Kluwer Academic Publishers, Dordrecht (2000)

\bibitem{Pugliese}
Sergeyev, Ya.D., Famularo, D., Pugliese, P.: Index Branch-and-Bound Algorithm for Lipschitz univariate global optimization with multiextremal constraints. J. Glob. Optim. 21(3), 317--341 (2001)

\bibitem{Barkalov2002}
Barkalov, K.A., Strongin, R.G.: A global optimization technique with an adaptive order of checking for constraints. Comput. Math. Math. Phys. 42(9), 1289--1300 (2002)

%\bibitem{Strongin2003} Strongin, R.G., Sergeyev, Ya.D.: Global optimization: fractal approach and non-redundant parallelism. J. Glob. Optim. 27(1), 25--50 (2003)

%\bibitem{Barkalov2010} Barkalov, K., Ryabov, V., Sidorov, S.: Parallel Scalable Algorithms with Mixed Local-Global Strategy for Global Optimization Problems. In: Malyshkin, V. (Ed.) MTPP 2010, LNCS. 6083, 232--240 (2010)

%\bibitem{Barkalov2014} Barkalov, K.A., Gergel, V.P.: Multilevel scheme of dimensionality reduction for parallel global search algorithms. In: Proceedings of the 1st International Conference on Engineering and Applied Sciences Optimization -- OPT-i 2014. pp. 2111--2124 (2014)

\bibitem{Barkalov2015}
Barkalov, K., Gergel, V., Lebedev, I.: Use of Xeon Phi Coprocessor for Solving Global Optimization Problems. In: Malyshkin, V. (Ed.) PaCT 2015, LNCS. 9251, 307--318 (2015)

\bibitem{Barkalov2016}
Barkalov, K., Gergel, V.: Parallel Global Optimization on GPU. J. Glob. Optim. 66(1), 3--20 (2016)

%\bibitem{Lebedev2016}Barkalov, K., Gergel, V., Lebedev, I.: Solving Global Optimization Problems on GPU Cluster. In: Simos T.E. (Ed.) ICNAAM 2015, AIP Conference Proceedings. 1738, art. no. 400006 (2016)

\end{thebibliography}

>>>>

\begin{abstract}
Abstract.
\end{abstract}

% Head 1
\section{INTRODUCTION}

In the present paper, the methods for generating the global optimization test problems with non-convex constraints
\begin{eqnarray}
&\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}}, \label{i_problem} \\
&D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\} \label{D}
\end{eqnarray}
are considered. The objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and the left-hand sides $g_i(y), \; 1\leq i \leq m,$ of the constraints are supposed to satisfy the Lipschitz condition
\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1. \]
with the Lipschitz constants unknown a priori. The analytical formulae of the problem functions may be unknown, i.e. these ones may be defined by an algorithm for computing the function values in the search domain (so called ``black-box''-functions). It is supposed that even a single computing of a problem function value may be a time-consuming operation since it is related to the necessity of numerical modeling in the applied problems (see, for example, \cite{Menniti2008,Kvasov2015,Modorskii2017}).

The evaluation of efficiency of the developed methods is one of the key problems in the optimization theory and applications. Unfortunately, it is difficult to obtain any theoretical estimates in many cases. As a result, the comparison of the methods is performed by carrying out the computational experiments on solving some test optimization problems in most cases. In order to obtain a reliable evaluation of the efficiency of the methods, the sets of test problems should be diverse and representative enough. The problem of choice of the test problems has been considered in a lot of works (see, for example, \cite{Floudas1999,Gaviano2003,Ali2005,Addis2007}). Unfortunately, in many cases, the proposed sets contain a small number of test problems, and it is difficult to obtain the problems with desired properties. The most important drawback consists of the fact that the constraints are absent in the proposed test problems as a rule (or the constraints are relatively simple: linear, convex, etc.).

@@

%One generator for random samples of two-dimensional test functions has been described in \cite{Grishagin1978,Grishagin2016}. This generator produces two-dimensional functions according to the formula
%\begin{eqnarray} \nonumber \label{VAG}
%\varphi(y)= -&\left\{\left(\sum^{7}_{i=1}\sum^{7}_{j=1}A_{ij}g_{ij}(y)+B_{ij}h_{ij}(y)\right)^2+\right. \\
%&\left.\left(\sum^{7}_{i=1}\sum^{7}_{j=1}C_{ij}g_{ij}(y)+D_{ij}h_{ij}(y)\right)^2\right\}^{1/2},\\ \nonumber
%\end{eqnarray}
%where $g_{ij}(y)=\sin(i\pi y_1)\sin(j\pi y_2)$, $h_{ij}(y)=\cos(i\pi y_1)\cos(j\pi y_2)$, $y=(y_1,y_2)\in R^2, \; 0 \leq y_1,y_2 \leq 1$, and coefficients $A_{ij}, B_{ij}, C_{ij}, D_{ij}$  are taken uniformly in the interval $[-1,1]$.

@@

\section{Numerical results}

@@

The index method has been proposed and developed in \cite{Strongin2000,Sergeyev2001,Barkalov2002}. The approach is based on a separate accounting for each constraint of the problem and is not related to the use of the penalty functions. According to the rules of index method, every iteration includes a sequential checking of fulfillment of the problem constraints at this point. The first occurrence of violation of any constraint terminates the trial and initiates the transition to the next iteration. This allows: (i) accounting for the information on each constraint separately and (ii) solving the problems, in which the function values may be undefined out of the feasible domain.  It should be noted, that the index method can be efficiently parallelized for accelerators \cite{Barkalov2015,Barkalov2016}.

@@

The developed approach allows generating any number of test global optimization problems with non-convex constraints for performing multiple computational experiments in order to obtain a reliable evaluation of the efficiency of the developed optimization algorithms.

% Acknowledgement
\section{ACKNOWLEDGMENTS}
This research was supported by the Russian Science Foundation, project No 16-11-10150.

% References

%\nocite{*}
\bibliographystyle{aipnum-cp}%
\bibliography{LeGo}%
